---
title: "Introduction to mfmsbm"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to mfmsbm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Overview

The **mfmsbm** package implements a collapsed Gibbs sampler for Bayesian
community detection in networks using the Mixture of Finite Mixtures of
Stochastic Block Models (MFM-SBM) framework. It supports two priors on the
number of components:

- **Zero-truncated Poisson** (Miller and Harrison, 2018)
- **Gnedin** (Gnedin, 2010)

## Quick Start

### Generate a synthetic network

```{r}
library(mfmsbm)

set.seed(42)
sbm <- generate_sbm(n = 100, K = 3, p = 0.5, q = 0.1, type_network = "balanced")
```

### Run the Gibbs sampler (Poisson prior)

```{r}
gamma_ <- 1
n <- 100
logVn <- log_vn_miller(gamma_, n, n + 10, lambda = 1)
z_start <- c(sample(1:9, 9), sample(1:9, n - 9, replace = TRUE))

fit <- cogibbs_poisson(
  M = 500, K_start = 9, A = sbm$A0, n = n,
  a = 1, b = 1, gamma_ = gamma_, logVn_miller = logVn, z_start = z_start
)
```

### Post-processing

```{r}
burn_in <- 200
cc <- coclustering_matrix(fit$z_post[, (burn_in + 1):500])

# Point estimate using VI minimization (requires mcclust.ext)
if (requireNamespace("mcclust.ext", quietly = TRUE)) {
  memb <- mcclust.ext::minVI(cc, method = "avg", max.k = 20)$cl
  table(memb)
}
```

## References

- Geng, J., Bhattacharya, A., and Pati, D. (2019). "Probabilistic community
  detection with unknown number of communities." *JASA*, 114(526), 893--905.
- Miller, J. W. and Harrison, M. T. (2018). "Mixture models with a prior on
  the number of components." *JASA*, 113(521), 340--356.
